Single-cell virus sequencing of influenza variants that trigger innate immunity

### 2018-09-04 paper/paper.tex
added outline of initial Methods

\figdata{Genbank files giving the sequences of the wildtype and synonymously barcoded viruses are in \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/data/flu_sequences/flu-wsn.gb} and \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/data/flu_sequences/flu-wsn-double-syn.gb}.}
\label{seqs}

@@

>>>>

\figdata{Genbank files giving the sequences of the wildtype and synonymously barcoded viruses are in \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/data/flu_sequences/flu-wsn.gb} and \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/data/flu_sequences/flu-wsn-double-syn.gb}.}
\label{figdata:virus_seqs}

@@

\subsection{IFN reporter cell lines}
\jdbcomment{Alistair writes this}
Reporter sequences \FIGDATA[IFNrare]{reporter_sequences}

\subsection{Viral stocks}
\jdbcomment{Alistair writes this}
Wildtype and synonymously barcoded viruses in \FIGDATA[experiment]{virus_seqs}

\subsection{Single-cell infections and transcriptomics using 10X Chromium on IFN-enriched cells}
\jdbcomment{Alistair writes this}

\subsection{Enrichment and preparation of viral cDNA for PacBio sequencing}
\jdbcomment{Alistair writes this}

\subsection{Computational analysis of single-cell transcriptomic and PacBio data}
\jdbcomment{Jesse writes this}
